The SMT Competition 2015--2018

### 2019-08-21 2018/report/SMT-COMP.tex
Minor

It is interesting to note that the non-competing solvers MathSAT and
Z3 often appear as the best performing solver.  We view this as
confirmation of the industrial significance of competition results.
Both solvers are industrial-strength tools, actively maintained and
tuned.  The reasons for non-entry into the competition are orthogonal
to their suitability for the competition.  Indeed, Z3 has been entered
into the competition competitively in the past, and one can assume
that it was trained on the current problems.  The fact that
industrial-strength solvers perform well in the competition supports
the notion that the benchmarks in the competition are industrially
relevant.

>>>>

It is interesting to note that the non-competing solvers MathSAT and
Z3 often appear as the best performing solver.  We view this as
confirmation of the industrial significance of the competition
results.  Both solvers are industrial-strength tools, actively
maintained and tuned for applications.  The reasons for non-entry into
the competition are orthogonal to their suitability for the
competition.  Indeed, Z3 has been entered into the competition
competitively in the past, and one can assume that it was trained on
the current problems.  The fact that industrial-strength solvers
perform well in the competition supports the notion that the
benchmarks in the competition are industrially relevant.
